Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
BCP: be more conservative

Some time later however, the one person in our team that knows
more about Haskell than we do, convinces us that throwing exceptions
from pure code is considered poor design. Hence, we change the
specification so that negative input values should result in zero.

>>>>

At some point, we realize that throwing an exception on invalid input
is not suitable for our use-case.  Hence, we change the specification,
so that negative input values should result in zero.
